Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-18 nips_2018.tex
add list times
add list dataset to supplement
add lists curve
finish list section

\subsection{List Processing}\label{listSection}
Synthesizing programs that manipulate data structures is a widely studied
problem in the programming languages community~\cite{feser2015synthesizing}.
%with applications to computer aided programming~\cite{solar2008program}.
We consider this problem within the context of learning functions that
manipulate lists with some involvement of numerical arithmetic.

\begin{wrapfigure}{r}{0.55\textwidth}\centering
  \begin{tabular}{lll}
    \toprule
    Name & Input & Output \\\midrule
    repeat-2 & [7\, 0] & [7\, 0\, 7\, 0] \\
    drop-3 & [0\, 3\, 8\, 6\, 4] & [6\, 4] \\
    rotate-2 & [8\, 14\, 1\, 9] & [1\, 9\, 8\, 14] \\
    count-head-in-tail & [1\, 2\, 1\, 1\, 3] & 2 \\
    keep-mod-5 & [5\, 9\, 14\, 6\, 3\, 0] & [5\, 0] \\
    product & [7\, 1\, 6\, 2] & 84 \\
    \bottomrule
  \end{tabular}
  \captionof{table}{Some tasks in our list function domain}
  \label{listexamples}
\end{wrapfigure}
We created 236 human-interpretable list manipulation tasks, each with 15
input/output examples (Tbl.~\ref{listexamples}).
Our data set is challenging in three major ways: many of the tasks require
complex solutions, the tasks were not generated from some latent DSL, and
the agent must learn to solve these complicated problems from only 236
tasks.
Our data set assumes arithmetic operations as well as sequence operations,
so we additionally provide our system with the following arithmetic
primitives: \code{mod}, \code{*}, \code{>}, \code{is-square},
\code{is-prime}.

@@

  \\\midrule\multicolumn{7}{c}{\emph{List Processing}}\\\midrule
  \% solved&\textbf{86\%} &84\% &&60\%&74\%&70\%\\
  Solve time&  0.8s&0.7s&&1.0s&1.0s&1.1s

@@

\begin{figure}\centering
\includegraphics[width = 3.5cm]{figures/rationalCurve.eps} 
  \includegraphics[width = 3.5cm]{figures/list.eps}
  \includegraphics[width = 3.5cm]{figures/textLearningCurve.eps}        
  \caption{Learning curves for \system both with (blue) and without (red) the recognition model. Solid lines: \% holdout testing tasks solved. Dashed lines: Average solve time.}\label{learningCurves} 
\end{figure}

>>>>

\subsection{List Processing}\label{listSection}
Synthesizing programs that manipulate data structures is a widely studied
problem in the programming languages community~\cite{feser2015synthesizing}.
%with applications to computer aided programming~\cite{solar2008program}.
We consider this problem within the context of learning functions that
manipulate lists with some involvement of integer arithmetic.

\begin{wrapfigure}{r}{0.55\textwidth}\centering
  \begin{tabular}{lll}
    \toprule
    Name & Input & Output \\\midrule
    repeat-2 & [7\, 0] & [7\, 0\, 7\, 0] \\
    drop-3 & [0\, 3\, 8\, 6\, 4] & [6\, 4] \\
    rotate-2 & [8\, 14\, 1\, 9] & [1\, 9\, 8\, 14] \\
    count-head-in-tail & [1\, 2\, 1\, 1\, 3] & 2 \\
    keep-mod-5 & [5\, 9\, 14\, 6\, 3\, 0] & [5\, 0] \\
    product & [7\, 1\, 6\, 2] & 84 \\
    \bottomrule
  \end{tabular}
  \captionof{table}{Some tasks in our list function domain. See the
  supplement for the complete data set.}
  \label{listexamples}
\end{wrapfigure}
We created 236 human-interpretable list manipulation tasks, each with 15
input/output examples (Tbl.~\ref{listexamples}).
Our data set is challenging in three major ways: many of the tasks require
complex solutions, the tasks were not generated from some latent DSL, and
the agent must learn to solve these complicated problems from only 236
tasks.
Our data set assumes arithmetic operations as well as sequence operations,
so we additionally provide our system with the following arithmetic
primitives: \code{mod}, \code{*}, \code{>}, \code{is-square},
\code{is-prime}.

We experimented with \system by randomly splitting the data set into two
equal-sized parts: one for training, and one held out for testing.
We found that the recognition model provided no benefit for the training
tasks. However, it yielded faster search times on held out tasks allowing
more tasks to be solved before timing out.
Several inventions were produced to yield a more expressive DSL for the
domain (left of Tbl.~\ref{initialExampleDSL}, right of
Fig.~\ref{fragmentExample}). See the supplement for a complete list of
inventions.

@@

  \\\midrule\multicolumn{7}{c}{\emph{List Processing}}\\\midrule
  \% solved&\textbf{79\%} &76\% &71\%&35\%&62\%&37\%\\
  Solve time&  4.1s&5.8s&10.6s&34.7s&43.4s&20.2s
  %NOTE: "Ours" result was without helmholtz

@@

\begin{figure}\centering
  \includegraphics[width = 3.5cm]{figures/list.eps}
  \includegraphics[width = 3.5cm]{figures/textLearningCurve.eps}        
  \includegraphics[width = 3.5cm]{figures/rationalCurve.eps} 
  \caption{Learning curves for \system both with (blue) and without (red) the recognition model. Solid lines: \% holdout testing tasks solved. Dashed lines: Average solve time.}\label{learningCurves} 
\end{figure}
